Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-04 Paper/paper.tex
New title and abstract

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{\todo{How's this title?}A Workflow for Developers New to Web Application Testing} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.} \othermemberA{Franz Kurfess, Ph.D.} \othermemberB{David Janzen, Ph.D.} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
Web applications are quickly replacing standalone applications. As with any type of application, these web applications need to be tested to ensure proper functionality and reliability. There have been substantial efforts to create tools to help with the testing of web applications but there is, as of yet, no standard set of tools or recommended workflow to insure speed of development and strength of application.

We have brought together a number of testing tools from the web and created what we feel is a fully-featured, easy to use, testing framework and workflow for JavaScript web applications.
\end{abstract}

>>>>

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{Creating a Testing Framework and Workflow for Developers New to Web Application Engineering} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.} \othermemberA{Franz Kurfess, Ph.D.} \othermemberB{David Janzen, Ph.D.} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
Web applications are quickly replacing standalone applications for everyday tasks. These web applications need to be tested to ensure proper functionality and reliability. There have been substantial efforts to create tools that assist with the testing of web applications but there is, as of yet, no standard set of tools or a recommended workflow to ensure speed of development and strength of application.

We have used and outlined the merits of a number of existing testing tools and brought together the best among them to create what we feel is a fully-featured, easy to use, testing framework and workflow for web applications.

We then took an existing web application, PolyXpress, and augmented its development process to include our workflow suggestions in order to incorporate testing at all levels. PolyXpress is a web application that ``allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} After incorporating our testing procedures, we immediately detected previously unknown bugs in the software. In addition, there is now a workflow in place for future developers to use which will expedite their testing and development.
\end{abstract}
